Analysis for Project

### 2021-11-22 analysis/analysis.Rmd
Add sex to model to address issue #21

0.  Raw race differences
1.  Add fixed effects for state, current grade, year, and metro
2.  Add kids and parents foreign-born status.
3.  Add mother and father highest degree
4.  Add family income (square rooted), own your own home, and whether parents are married.

@@

```{r build-models, results='asis'}
model0 <- glm(below_exp_grade~race, data=acs, family=binomial)
model1 <- update(model0, .~.+as.factor(year)+current_grade+as.factor(state)+metro)
model2 <- update(model1, 
                 .~.+foreign_born+foreign_born_mother+foreign_born_father+
                   spk_eng+spk_eng_mother+spk_eng_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)

>>>>

0.  Raw race differences
1.  Add fixed effects for state, current grade, year, metro, and sex
2.  Add kids and parents foreign-born status.
3.  Add mother and father highest degree
4.  Add family income (square rooted), own your own home, and whether parents are married.

@@

```{r build-models, results='asis'}
model0 <- glm(below_exp_grade~race, data=acs, family=binomial)
model1 <- update(model0, 
                 .~.+as.factor(year)+current_grade+as.factor(state)+metro+sex)
model2 <- update(model1, 
                 .~.+foreign_born+foreign_born_mother+foreign_born_father+
                   spk_eng+spk_eng_mother+spk_eng_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)
